Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Beta diversity

```{r vegdist, eval = FALSE}

phf_profile.rel <- microbiome::transform(pseq_filtered, 'compositional')
otu <- microbiome::abundances(phf_profile.rel)

if (!file.exists("rds/bray.dist.m.rds")) {
    bray.dist.m <- vegdist(t(otu), method="bray")
    saveRDS(bray.dist.m, file = "rds/bray.dist.m.rds")
} else {
    bray.dist.m <- readRDS("rds/bray.dist.m.rds")
}

dist.matrix <- as.matrix(bray.dist.m)
attr(dist.matrix, "method") <- "bray"

>>>>

```{r vegdist}
calculate.beta.matrix <- function(pseq) {
    compositional.profile <- microbiome::transform(pseq, 'compositional')
    otu <- microbiome::abundances(compositional.profile)
    vegan::vegdist(t(otu), method="bray")
}

if (!file.exists("rds/bray.dist.m.species.rds") || !file.exists("rds/bray.dist.m.genus.rds") {
    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
    saveRDS(bray.dist.m.species, file = "rds/bray.dist.m.species.rds")
    bray.dist.m.genus <- calculate.beta.matrix(pseq.genus)
    saveRDS(bray.dist.m.genus, file = "rds/bray.dist.m.genus.rds")
} else {
    bray.dist.m.species  <- readRDS("rds/bray.dist.m.species.rds")
    bray.dist.m.genus <- readRDS("rds/bray.dist.m.genus.rds")
}
}
```

```{r temp}
dist.matrix <- as.matrix(bray.dist.m)
attr(dist.matrix, "method") <- "bray"
```
